% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  16,
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage[]{libertine}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=10mm,left=15mm,right=15mm,bottom=5mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage{multicol}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage{libertine}
\pagestyle{empty}
\setlength{\multicolsep}{2pt plus 1.0pt minus 0.75pt}% 50% of original values
\setlength{\columnsep}{3em}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}

\begin{document}


\begin{huge}\begin{center}{\bf Shangxuan Zhong}\end{center}\end{huge}

\begin{center}Email: zhongsx@bu.edu , zhongshangxuan@gmail.com \\
Phone: +1 6179032034 , +86 17740940442 \\
Address:  525 Lincoln St., Apt 309, Boston, MA \\
\end{center}
\vspace{15pt}

\begin{large}
  {\bf Education}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
    \begin{flushleft}{\bf University of Toronto}\end{flushleft}
    \begin{flushright}Sep. 2020 - Jun. 2024\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}Bachelor of Mathematics, Statistics, Computer Science\end{flushleft}
  \end{multicols}
  \vspace{-0.20cm}
\end{large}

\begin{itemize}
\tightlist
\item
  \textbf{Relevant Courses}: Linear Algebra, Advanced Algebra, Ordinary
  Differential Equations, Probability Theory, Partial Differential
  Equation, Advanced Calculus, Software Design, Financial Principles,
  Actuarial Science, Complex Variables, Computer Organization, Time
  Series Analysis, Machine Learning, Big Data Analytics
\end{itemize}

\vspace{0.2cm}

\begin{large}
  \begin{multicols}{2}
    \begin{flushleft}{\bf Boston University}\end{flushleft}
    \begin{flushright}Sep. 2024 - Aug. 2025\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}Master of Applied Business Analytics\end{flushleft}
  \end{multicols}
  \vspace{-0.20cm}
\end{large}

\begin{itemize}
\tightlist
\item
  \textbf{Relevant Courses}: Business Analytics, Operations Management,
  Financial Concepts, Decision Making, Enterprise Risk Analytics,
  Marketing Analytics, Database Management, Big Data Applications, Web
  Design
\end{itemize}

\vspace{2pt}

\begin{large}{\bf Internship Experience}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
  \parbox{1.4\linewidth}{\bf Xin'an Chemical Group Co., Ltd.}
    \begin{flushright}Jun. 2021 - Jul. 2021\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Project Manager Assistant}\end{flushleft}
    \begin{flushright}  \end{flushright}\end
  {multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Assisted the IT and Process Innovation Department in developing a
  digital marketing plan for new chemical products.
\item
  Conducted market research, feasibility analysis (market competition,
  demand, etc.), and project positioning analysis.
\item
  Participated in team meetings and brainstorming sessions, assisted in
  drafting proposal presentations, and provided actionable
  recommendations.
\item
  Attended exchange meetings with Wanhua Chemical Group, documented
  meeting minutes, and proposed suggestions for product innovation and
  market competitiveness enhancement.
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \parbox{1.4\linewidth}{\bf Shanghai Fuwai Brand Planning Co., Ltd.}
    \begin{flushright}May 2022 - Jun. 2022\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Corporate Brand and Culture Consulting Intern}\end{flushleft}
    \begin{flushright}  \end{flushright}\end
  {multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Analyzed corporate brand image and culture, including logos, slogans,
  goals, visions, and corporate spirit.
\item
  Assisted in designing a digital transformation plan and cultural shift
  for Guest Bank, based on its current status and culture.
\item
  Conducted research and analysis on the corporate culture of Jinsin
  Company (a subsidiary of Yuntianhua Group) and proposed specific
  improvements for its slogans, goals, and corporate spirit.
\item
  Researched the development trends of China's banking industry,
  analyzed differences among representative banks, and proposed future
  development directions.
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \parbox{1.4\linewidth}{\bf Ernst & Young (China) Advisory Co., Ltd.}
    \begin{flushright}Jun. 2022 - Jul. 2022\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Technology and Financial Consulting Intern}\end{flushleft}
    \begin{flushright}  \end{flushright}\end
  {multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Participated in the SAP Phase III project for Xin'an Chemical Group as
  part of the finance and technology teams.
\item
  Assisted the financial analysis team in researching, collecting, and
  summarizing data related to procurement, logistics, pricing, sales,
  and exports.
\item
  Supported the technology development team in building SAP and ERP
  systems, contributing to the development of the CO (Controlling) and
  SD (Sales and Distribution) modules.
\item
  Served as a key user for internal testing to ensure smooth system
  operation post-launch.
\end{itemize}

\vspace{7pt}

\begin{large}
  \begin{multicols}{2}
    \parbox{1.4\linewidth}{\bf Hangzhou City Brain Technology and Service Co., Ltd.}
    \begin{flushright}Jul. 2022 - Aug. 2022\end{flushright}
  \end{multicols}
  \vspace{-0.17cm}
  \begin{multicols}{2}
    \begin{flushleft}\textit{Big Data Development Intern}\end{flushleft}
    \begin{flushright}  \end{flushright}\end
  {multicols}
\end{large}
\vspace{-0.16cm}

\begin{itemize}
\tightlist
\item
  Learned operations related to the MaxCompute (ODPS) big data
  development platform.
\item
  Acquired knowledge of commonly used big data software and its
  significance in development.
\item
  Assisted in data governance for multiple projects based on specific
  requirements.
\item
  Learned about building data warehouses, collecting and organizing
  data, and providing data models to support departmental queries and
  development needs.
\end{itemize}

\vspace{7pt}

\begin{large}{\bf Publications}
  \vspace{3pt}
  \hrule
  \begin{multicols}{2}
  \parbox{1.6\linewidth}{\bf Paper: Exploring Correlations Between Economic Indicators with Natural and Societal Factors Based on Linear Regression Model}
    \begin{flushright}Published Jan., 2024\end{flushright}
  \end{multicols}
\end{large}
\vspace{-0.16cm}

\textbf{Description}: Utilized ``Global Country Information Dataset
2023'' to address the limitations of single-factor studies on economic
development drivers. Employed Pearson correlation coefficients to screen
key variables (e.g., land area, military size, carbon emissions) and
constructed a multi-factor collaborative impact analysis framework using
OLS and FMOLS linear regression models. Quantified the integrated
effects of natural and social factors on national economic development
and validated the model's predictive performance using machine learning
training-test set methods. Published during studies at the University of
Toronto, providing a data-driven reference for macroeconomic
policy-making.

\vspace{7pt}

\begin{large}{\bf Skills}
  \vspace{3pt}
  \hrule
\end{large}

\textbf{Technical Skills}: Microsoft Office, Python, Java, SQL, C, R
\textbf{Language Skills}: Mandarin, English, Japenese (High to low
proficiency)

\begin{large}{\bf Self-Evaluation}
  \vspace{3pt}
  \hrule
\end{large}

\begin{itemize}
\tightlist
\item
  Highly motivated with a strong sense of responsibility and attention
  to detail.
\item
  Excellent analytical skills and logical thinking, proficient in office
  software.
\item
  Strong team player with effective communication skills, capable of
  identifying and solving problems.
\item
  Quick learner, adaptable to new knowledge and challenges, and eager to
  take on new tasks.
\end{itemize}




\end{document}
